### 2016-04-14 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Changes all over the place

The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
This is done by truncating the associated impulse response, as in~\citep{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction. 
The truncation point (cut-off index) is determined by one of two statistically inspired methods.
It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.

Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
A \gls{SISO} \gls{LTI} system is considered.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
\begin{equation}\label{eq:nparam:trunc:LPM:TD}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).

@@

Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector  \citep{Ljung1999,Soderstrom1989}. 
In this section, however, a nonparametric technique is developed, and formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.

@@

\item The work in this section is for discrete-time systems. Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.

\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.

\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.

@@

The rest of the section is structured as follows. 
\secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{se:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_\text{poly}(\Omega_k)$.

These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\Omega_k)$.
Discussion of the simulation results is then followed by a conclusion in \secref{se:conclusion}.

\subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}
\label{se:theoryLPMandWindowing}

Details of the theory pertaining to this section may be found in \citep{Schoukens2009LPM}, basic aspects of which are presented below.

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an OE setup (\figref{lpmtdrep}):
\begin{assumption}
The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

\begin{assumption}

The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, for example $U_0(k+1) - U_0(k)$ should not vanish to zero. %i.e. $U_0(k+1) - U_0(k) \neq 0$.
\TODO{assumption is not complete! some expectation is missing!}
\end{assumption}

@@

\begin{assumption}
The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known.
\end{assumption}

\begin{assumption}
The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
\end{assumption}

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

@@

When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
\begin{align}
G_0(\Omega_{k+r})
  &\approx 
  G_0(\Omega_k)+g_1r+g_2r^2
  \label{eq:lpm:expansionG:quadratic}
\\
  T(\Omega_{k+r})
    &\approx 
    T(\Omega_k)+t_1r+t_2r^2
    \label{eq:lpm:expansionT:quadratic}
\end{align}
with ($r\in\mathbb{W}_3$) and the vector of parameters:
\begin{equation}\label{lpmThetaEst}
\theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
\end{equation}
The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
\begin{equation}
\hat{G}_\text{poly}(\Omega_k) = \hat\theta_1(k)
\end{equation}

The estimation of $\hat{G}_\text{poly}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}

   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
   A small band is selected (gray area), in which $\hat G_\mathrm{poly}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_\mathrm{poly}(\Omega_k)$ (white circle) is retained. This procedure is repeated for all frequencies $\Omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_\text{poly}(\Omega_k)$.

\section{Smoothing the \gls{FRF} estimate}
\label{se:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{\mathrm{poly}}(\Omega_k)$) from \secref{se:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_\mathrm{poly}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{\mathrm{poly}}(\Omega_k)$.

@@

\begin{assumption}
The estimate $\hat G_\mathrm{poly}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
\end{assumption}

@@

The estimated impulse response function  $\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_\mathrm{poly}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:

\begin{align}\label{eq:impRespiDFT}
\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_\mathrm{poly}(\Omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}
where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:

\begin{align}
\hat G_\mathrm{poly}(\Omega_{N-k}) = \overline{\hat G_\mathrm{poly}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}
(with $\conj{\hat G_\mathrm{poly}}$ the complex conjugate of $\hat G_\mathrm{poly}$) to ensure $\hat g_\mathrm{poly}(t)$ to be real.

\TODO{fix reference Section II}
Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. Unfortunately, the \gls{LPM} presented in \secref{se:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e. \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
This limitation is lifted by developing a simple estimator of the mean value, presented below.

\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{se:DCvalueEst}
The correct mean value of the impulse response accounts for (i.e. estimates) the \gls{DC} value of the \gls{FRF}. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

@@

\begin{enumerate}
\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)$, estimated by the \gls{LPM}, as %$\hat g_\mathrm{poly}(t)$ as
\begin{align}
m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)
\end{align}

\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{\mathrm{poly}\setminus \mathrm{DC
}}(t)$ to obtain the improved impulse response $\hat g_\mathrm{poly}(t)$, \emph{viz}:

\begin{align}
\hat g_\mathrm{poly}(t) = \hat g_{\mathrm{poly}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}
\end{enumerate}

\subsection{Truncation Via the $F$-Test}
\label{sec:nonparametric:truncation:ftest}
To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_\mathrm{poly}$ is split into smaller segments. 
One can then gradually determine whether these segments are noise or the actual impulse response.

@@

\begin{enumerate}
  \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. 
If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

@@

\end{enumerate}
This procedure is illustrated in \figref{fig:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.

\begin{figure}[tbh]
\centering
 \setlength\figurewidth{0.68\columnwidth}
 \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/truncRMS.tikz}
\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.}
\label{fig:nonparametric:truncation:Ftest}
\end{figure}

@@

\begin{enumerate}
\item Obtain the estimate of the impulse response $\hat g_\mathrm{poly}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{se:DCvalueEst}. 
Henceforth, $\hat g_\mathrm{poly}(t)$ will simply be denoted as $\hat g(t)$.

@@

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/expfit.tikz}
\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response $g(t)$ via the fit of  an exponential through the peaks of $\abs{g(t)}$ that are above $5\noiseStd$ with $\noiseStd$ is the estimated noise level, as per \eqref{eq:TmaxDef}.}
\label{fig:nonparametric:trunc:impresp:expfit}
\end{figure}

@@

The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
The result is depicted in \figref{fig:nonparametric:trunc:impresp:expfit}. 
An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line). The truncation time (black vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e. $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).

@@

\subsection{Simulation Results}\label{se:simResults}

\figref{figLPMvsTrunc} and \figref{fig:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
\\
y(t) &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.

\begin{figure}
    \centering
    \setlength\figurewidth{0.85\columnwidth}
    \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/figLPMvsTrunc.tikz}
    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{The bias $\sampleBias{\placeholder}$ and standard deviation $\sampleStd{\placeholder}$ of the \gls{FRF} estimates using both the \gls{LPM} (blue) and truncated~\gls{LPM} (red) are shown. 
    It can be seen that the truncation reduces the variance at the cost of an increased bias, however, the overall \gls{RMS} error is reduced by the truncation.}
    \label{figLPMvsTrunc}
\end{figure}

In \figref{figLPMvsTrunc} one observes the following:
\begin{itemize}
\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed. %i.e. a decrease of the black crosses w.r.t.~the gray ones is observed.

@@

\TODO{write about boxcar average, add reference}

>>>>

The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
This is done by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction. 
The truncation point (cut-off index) is determined by one of two statistically inspired methods.
It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.

Based on \citet{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
A \gls{SISO} \gls{LTI} system is considered.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
\begin{equation}\label{eq:nparam:trunc:LPM:TD}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).

@@

Numerous parametric identification techniques are devoted to the development of parametric plant $G(q,\theta)$ and noise models  $H(q,\theta)$, where  $\theta$ is the model parameters vector~\citep{Ljung1999,Soderstrom1989}. 
In this section, however, a nonparametric technique is developed, and formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.

@@

\item The work in this section is for discrete-time systems. 
Denote the $k^{\text{th}}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}k\fs/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.

\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{\text{th}}$ frequency.

\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{\text{th}}$ frequency.

@@

The rest of the section is structured as follows. 
\secref{sec:nparam:trunc:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\Omega_k)$.

These FRF estimates are also compared with the true \gls{LTI} system ${G}_0(\Omega_k)$.
Discussion of the simulation results is then followed by a conclusion in \secref{sec:nparam:trunc:conclusion}.

\subsection{Theory on the LPM and Windowing: \glsentrytext{OE} Setup}
\label{sec:nparam:trunc:theoryLPMandWindowing}

Details of the theory pertaining to this section may be found in \citet{Schoukens2009LPM}, basic aspects of which are presented below.

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{lpmtdrep}):
\begin{assumption}
The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

\begin{assumption}
The spectrum of the  input signal $U_0$ is not a smooth function of the frequency, but a rough function, i.e. $U_0(k+1) - U_0(k)$ should not vanish to zero~\cite{Schoukens2009LPM}.
\end{assumption}

@@

\begin{assumption}
The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
\end{assumption}

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}
\label{sec:nparam:trunc:LPMFRFest}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is a popular choice.
In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. 
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

@@

When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\Omega_{k}$:
\begin{align}
G_0(\Omega_{k+r})
  &\approx 
  G_0(\Omega_k)+g_1r+g_2r^2
  \label{eq:lpm:expansionG:quadratic}
\\
  T(\Omega_{k+r})
    &\approx 
    T(\Omega_k)+t_1r+t_2r^2
    \label{eq:lpm:expansionT:quadratic}
\end{align}
with ($r\in\mathbb{W}_3$) and the vector of parameters:
\begin{equation}\label{lpmThetaEst}
\theta^{\TT}(k)=\left[G_0(\Omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
\end{equation}
The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
\begin{equation}
\hat{G}_{\LPM}(\Omega_k) = \hat\theta_1(k)
\end{equation}

The estimation of $\hat{G}_{\LPM}(\Omega_k)$ at a single frequency $\Omega_k = 0.586\unit{Hz}$ is illustrated in \figref{LPM_Schematic_EG}.% centered at $k$, where $r = 0$.
\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
   \setlength{\figurewidth}{0.8\columnwidth}
   \setlength{\figureheight}{0.68\figurewidth}

   \input{\thisDir/figs/LPMfig.tikz}
   \caption[Illustration of the LPM.]{Illustration of the \gls{LPM}. Top figures: input spectrum (left) and output spectrum (right). 
   A small band is selected (gray area), in which $\hat G_{\LPM}(\Omega_{k+r})$ is estimated (black thick line, bottom figure) as a local polynomial. Only its central value $\hat G_{\LPM}(\Omega_k)$ (white circle) is retained. This procedure is repeated for all frequencies $\Omega_k$.}
   \label{LPM_Schematic_EG}
\end{figure}
This procedure is repeated at each central frequency $\Omega_k$ for  $k\in \Set{1,\dots,N/2}$ (i.e. the entire frequency band, including Nyquist, but excluding \gls{DC}, and regularizing at the boundaries). This completes the \gls{LPM}, yielding an intrinsic averaging of the spectra of the estimated \gls{FRF}, $\hat{G}_{\LPM}(\Omega_k)$.

\section{Smoothing the \gls{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\Omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\Omega_k)$.

@@

\begin{assumption}
The estimate $\hat G_{\LPM}(\Omega_k)$ is available at all frequencies $\Omega_k$ for $k\in\{1,2,\dots,N/2\}$.
\end{assumption}

@@

The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\Omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:

\begin{align}\label{eq:impRespiDFT}
\hat g_{{\LPM}\setminus \mathrm{DC
}}(t) &= \frac{1}{\sqrt{N}}\sum_{k=1}^{N-1}\hat G_{\LPM}(\Omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}
where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:

\begin{align}
\hat G_{\LPM}(\Omega_{N-k}) = \overline{\hat G_{\LPM}(\Omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}
(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.

\TODO{fix reference Section II}
Smoothing of the estimated \gls{FRF} requires the correct estimate of the impulse response. Unfortunately, the \gls{LPM} presented in \secref{sec:nparam:trunc:theoryLPMandWindowing} and in \citep{Schoukens2009LPM} does not estimate the \gls{FRF}  at the frequency $\Omega_0$ (i.e. \gls{DC} value of the \gls{FRF}), hence the subscript $\setminus\mathrm{DC}$ in equation \eqref{eq:impRespiDFT}. Consequently, the mean value of the corresponding estimated impulse response given in equation \eqref{eq:impRespiDFT} is not correct. 
This limitation is lifted by developing a simple estimator of the mean value, presented below.

\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
The correct mean value of the impulse response accounts for (i.e. estimates) the \gls{DC} value of the \gls{FRF}. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

@@

\begin{enumerate}
\item Compute the mean value $m_{g10}$ of the last 10\% of the impulse response $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$, estimated by the \gls{LPM}, as %$\hat g_{\LPM}(t)$ as
\begin{align}
m_{g10} = \frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)
\end{align}

\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \emph{viz}:

\begin{align}
\hat g_{\LPM}(t) = \hat g_{{\LPM}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}
\end{enumerate}

\subsection{Truncation Via the $F$-Test}
\label{sec:nonparametric:truncation:ftest}
To distinguish the part of the measured impulse response where the actual impulse response dominates from the part where the noise dominates, the estimated impulse response $\hat{g}_{\LPM}$ is split into smaller segments. 
One can then gradually determine whether these segments are noise or the actual impulse response.

@@

\begin{enumerate}
  \item The impulse response $\hat{g}_{\LPM}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. 
If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

@@

\end{enumerate}
This procedure is illustrated in \figref{fig:nparam:trunc:nonparametric:truncation:Ftest} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{sec:nparam:trunc:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $\truncTime = 80$, beyond which all samples are set to zero, resulting in a smoothed \gls{FRF} estimate.

\begin{figure}[tbh]
\centering
 \setlength\figurewidth{0.68\columnwidth}
 \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/truncRMS.tikz}
\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response.}
\label{fig:nparam:trunc:nonparametric:truncation:Ftest}
\end{figure}

@@

\begin{enumerate}
\item Obtain the estimate of the impulse response $\hat g_{\LPM}(t)$ from the \gls{LPM}, corrected for its \gls{DC} value as discussed in \secref{sec:nparam:trunc:DCvalueEst}. 
Henceforth, $\hat g_{\LPM}(t)$ will simply be denoted as $\hat g(t)$.

@@

\begin{figure}[tbh] %top bottom here
\centering
\setlength\figurewidth{0.85\columnwidth}
\setlength\figureheight{0.68\figurewidth}
\input{\thisDir/figs/expfit.tikz}
\caption[Impulse response truncation using exponential fit.]{Truncation of the impulse response $g(t)$ via the fit of  an exponential through the peaks of $\abs{g(t)}$ that are above $5\noiseStd$ with $\noiseStd$ is the estimated noise level, as per \eqref{eq:TmaxDef}.}
\label{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}
\end{figure}

@@

The measured signal was disturbed by random white noise, $y(t) = y_0(t) + e(t)$, such that the \gls{SNR} was $14.2\unit{dB}$.
The result is depicted in \figref{fig:nparam:trunc:nonparametric:trunc:impresp:expfit}. 
An exponential function (black thick line) is fitted on the maxima (gray circles) of the absolute value of a noisy impulse response (dark gray line). The truncation time (black vertical line) $\truncTime$ was selected as the time instant at which the fitted exponential fell below $0.4\noiseStd$ (i.e. $\gamma = 0.4$ in equation \eqref{eq:truncTimeExpFit}).

@@

\subsection{Simulation Results}\label{sec:nparam:trunc:simResults}

\figref{fig:nparam:trunc:LPMvsTRunc} and \figref{fig:nparam:trunc:pdfAndRMSeVStruncTime} compare the \gls{LPM} with and without truncation of the impulse response.
Here, the truncation instant $\truncTime$ is determined using the exponential fitting method.
They were obtained from simulations on  the system described by the following simulation equations, which are relevant to the \gls{LPM} outlined in \secref{sec:nparam:trunc:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
\\
y(t) &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the \gls{SNR} of the output signal is $18.3\unit{dB}$.

\begin{figure}
    \centering
    \setlength\figurewidth{0.85\columnwidth}
    \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/figLPMvsTRunc.tikz}
    \caption[Comparison of FRF estimated using LPM and Truncated LPM.]{The bias $\sampleBias{\placeholder}$ and standard deviation $\sampleStd{\placeholder}$ of the \gls{FRF} estimates using both the \gls{LPM} (blue) and truncated~\gls{LPM} (red) are shown. 
    It can be seen that the truncation reduces the variance at the cost of an increased bias, however, the overall \gls{RMS} error is reduced by the truncation.}
    \label{fig:nparam:trunc:LPMvsTRunc}
\end{figure}

In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
\begin{itemize}
\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed. %i.e. a decrease of the black crosses w.r.t.~the gray ones is observed.

@@
